---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ncaavolleyballR

<!-- badges: start -->

<!-- badges: end -->

**ncaavolleyballR** is an R package for acquiring NCAA volleyball data.

## Installation

You can install the development version of ncaavolleyballR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tyler-widdison/ncaavolleyballR")
```

## Example (existing functions)

Get NCAA women's volleyball teams.

```{r example, warning=FALSE}
library(ncaavolleyballR)
ncaavolleyballR::ncaa_wvolleyball_teams()
```

Get NCAA women's volleyball schedules.

```{r TeamScheudle}
ncaavolleyballR::ncaa_wvolleyball_schedule('Yale', 813, 2017)
```

```{r ConfScheudle}
ncaavolleyballR::ncaa_wvolleyball_conf_schedule('Big Ten', 2022)
```

Get NCAA women's box score, single team for entire season.

```{r TeamBoxScore}
ncaavolleyballR::ncaa_wvolleyball_boxscore('BYU', 2015)
```

Get NCAA women's play by play, single team for entire season.

```{r}
ncaavolleyballR::ncaa_wvolleyball_pbp('BYU', 2021)
```
